ms_5

### 2020-04-26 ms_5.Rmd
just need to fix legends in app/titles

ggplot(ageopioidmodel, aes(year, number_of_deaths, color = age_range)) +
  geom_point() +
  scale_color_viridis_d() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Year", y = "Number of Opioid Deaths in America", color = "Age Range")

#raceopioid

@@

ggplot(raceopioidmodel, aes(year, opioid_deaths, color = race)) +
  geom_point() +
  scale_color_viridis_d() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Year", y = "Number of Opioid Deaths in America", color = "Race")
```

@@

# filtering data by race/age
ages0_24 <- ageopioidmodel %>%
  filter(age_range == "0-24")

@@

# averageageopioidmodel <- ageopioidmodel %>%
  # drop_na() %>%
  # group_by(age_range) %>%
  # summarize(mean_deaths = mean(number_of_deaths))

# averageageopioid_model <- lm(mean_deaths ~ age_range, data = averageageopioidmodel)
# averageageopioid_model %>%
  # tidy(conf.int = TRUE) %>%
  # select(term, estimate, conf.low, conf.high)
```

>>>>

@@

ageandracemodel <- ageopioidmodel %>%
  na.omit() %>%
  full_join(raceopioidmodel, by = "year") %>%
  rename(deathsbyage = number_of_deaths) %>%
  rename(deathsbyrace = opioid_deaths)

ggplot(ageandracemodel, aes(year, deathsbyage, color = age_range)) +
  geom_point() +
  scale_color_viridis_d() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Year", y = "Number of Opioid Deaths in America", color = "Age Range")

ggplot(ageandracemodel, aes(year, deathsbyrace, color = race)) +
  geom_point() +
  scale_color_viridis_d() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Year", y = "Number of Opioid Deaths in America", color = "Race")
```

```{r}
# filtering data by race to show effects of time on deaths in each race group

death_vs_white <- raceopioidmodel %>%
  filter(race == "White, Non-Hispanic")

death_vs_white %>%
    lm(opioid_deaths ~ year, data = .) %>% 
    tidy(conf.int = TRUE) %>% 
    select(term, estimate, conf.low, conf.high) %>%
    rename(Coefficient = estimate) %>%
    rename(`Lower End` = conf.low) %>%
    rename(`Upper End` = conf.high) %>%
    gt()

death_vs_black <- raceopioidmodel %>%
  filter(race == "Black, Non-Hispanic")

death_vs_black %>%
    lm(opioid_deaths ~ year, data = .) %>% 
    tidy(conf.int = TRUE) %>% 
    select(term, estimate, conf.low, conf.high)

death_vs_hispanic <- raceopioidmodel %>%
  filter(race == "Hispanic")

death_vs_hispanic %>%
    lm(opioid_deaths ~ year, data = .) %>% 
    tidy(conf.int = TRUE) %>% 
    select(term, estimate, conf.low, conf.high)
```

@@

# filtering data by age to show effects of time on deaths in each age group

ages0_24 <- ageopioidmodel %>%
  filter(age_range == "0-24")

@@

# looking at average deaths in each age group

averageageopioidbyage <- ageopioidmodel %>%
  drop_na() %>%
  group_by(age_range) %>%
  summarize(mean_deaths = mean(number_of_deaths))

# showing effects of being in each age group on number of deaths idt this makes sense

averageageopioid_model <- lm(number_of_deaths ~ age_range, data = ageopioidmodel)
averageageopioid_model %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high)
```
